\bf Faster Neural Machine Translation Inference

### 2018-02-02 fast-beam/fast-beam.tex
fast beam paper

Deep learning models are widely deployed for machine translation. In comparison on many other deep learning models, there are two characterisitics of machine translation which have not been adequately addressed by most software implementations, leading to slow inference speed. Firstly, as opposed to standard binary class models, machine translation models are used to discriminate between a large number of classes corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words in the target sentence. The sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for these issues which together, increase batched inference speed by up to ??? on modern GPUs without affecting model quality. For applications where the use of maxi-batching introduces unacceptable delays in response time, our work speed up inference speed by up to ???. Our work is applicable to other language generation tasks and beyond.

>>>>

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usualy contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or subwords in the target sentence. The sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which can increase batched inference speed by up to 41\% on modern GPUs without affecting model quality.
